[Standartox](http://standartox.uni-landau.de)

### 2019-06-29 talk/talk43.Rmd
added talk

---
title: "[Standartox](http://standartox.uni-landau.de)"
subtitle: "A tool for assessing the risk of chemicals"
author: "Andreas Scharmüller<br/>Verena C. Schreiner<br/>Ralf B. Schäfer<br/>"
institute: "Quantitative Landscape Ecology<br/>iES Landau, Institute for Environmental Sciences<br/>"
date: "1.7.2019 (updated: `r format(Sys.Date(), '%d.%m.%Y')`)"
output:
  xaringan::moon_reader:
    css: [metropolis, metropolis-fonts, default]
    #css: ['css/tweeks.css', metropolis, metropolis-fonts, default]
    #css: ['css/metropolis_as.css', 'css/metropolis-fonts_as.css', 'css/default.css']
    lib_dir: libs
    #classoption: "aspectratio=169"
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false # omits title slide
editor_options: 
  chunk_output_type: console
---

@@

Bernhardt et al. 2017
<img src="/home/scharmueller/Projects/etox-base/talk/data/bernhardt_et_al2.png" width="600px">

@@

---
background-image: url(/home/scharmueller/Projects/etox-base/talk/data/stream.jpg)
background-size: 450px
background-position: 90% 50%

@@

--
<br><br><br><br>
## Toxicity Data?

@@

--
<img src="/home/scharmueller/Projects/etox-base/talk/data/epa_ecotox_screenshot.png" width="1000px">

@@

<img src="/home/scharmueller/Projects/etox-base/talk/data/organigram2.png" width="1100px" style="position:absolute; left:10px; top:80px;">

@@

--
<img src="/home/scharmueller/Projects/etox-base/talk/data/standartox_screenshot.png" width="1000px">

@@

.pull-left[
- Filters

@@

  - Geometric mean
]

@@

.pull-right[
```{r fig.width=9, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_trichlorofon = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_trichlorofon_standartox_ppdb_comparison.rds'))
gg_trichlorofon
```
]

--
.pull-right[
__Result: Single EC50 value for a specific test setting__
]

@@

```{r fig.width=12, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_output.rds'))
gg_comparison
```

---
# Example: Comparison

```{r fig.width=12, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_ppdb_comparison.rds'))
gg_comparison
```

<img src="https://sitem.herts.ac.uk/aeru/ppdb/en/new_logo_small.jpg" width="300px" style="position:absolute; top:120px; right:150px;">

--
__92% of Standartox values diverge by less than a factor of 10 from PPDB values__

@@

<img src="http://3.bp.blogspot.com/-Wpp0vCJQDHo/U_ZMorXEynI/AAAAAAAAA7Y/Y-f-3brn99k/s1600/GBIF_logo_short_form.gif" width="120px" style="position:absolute; top:200px; right:70px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/worms.png" width="250px" style="position:absolute; top:300px; right:260px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/chebi.png" width="250px" style="position:absolute; top:450px; right:150px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/pubchem.png" width="250px" style="position:absolute; top:570px; right:200px;">

>>>>

---
title: "[Standartox](http://standartox.uni-landau.de)"
subtitle: "A tool for assessing the risk of chemicals"
author: "Andreas Scharmüller<br/>Verena C. Schreiner<br/>Ralf B. Schäfer<br/>"
institute: "Quantitative Landscape Ecology<br/>iES Landau, Institute for Environmental Sciences<br/>"
date: "1.7.2019 (updated: `r format(Sys.Date(), '%d.%m.%Y')`)"
output:
  xaringan::moon_reader:
    css: [metropolis, metropolis-fonts, default]
    #css: ['css/tweeks.css', metropolis, metropolis-fonts, default]
    #css: ['css/metropolis_as.css', 'css/metropolis-fonts_as.css', 'css/default.css']
    lib_dir: libs
    #classoption: "aspectratio=169"
    nature:
      ratio: '4:3'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false # omits title slide
editor_options: 
  chunk_output_type: console
---

@@

Bernhardt et al. 2017
<img src="/home/scharmueller/Projects/etox-base/talk/data/bernhardt_et_al_chem.png" width="260px">

@@

---
background-image: url(/home/scharmueller/Projects/etox-base/talk/data/stream.jpg)
background-size: 375px
background-position: 90% 50%

@@

--
<br><br><br><br>
### Toxicity Data?

@@

--
<img src="/home/scharmueller/Projects/etox-base/talk/data/epa_ecotox_screenshot.png" width="800px">

@@

<img src="/home/scharmueller/Projects/etox-base/talk/data/organigram2.png" width="850px" style="position:absolute; left:10px; top:130px;">

@@

--
<img src="/home/scharmueller/Projects/etox-base/talk/data/standartox_screenshot.png" width="800px">

@@

- Filters

@@

  - Geometric mean

```{r fig.width=8, fig.height=6, echo=FALSE, warning=FALSE, message=FALSE}
gg_trichlorofon = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_trichlorofon_standartox_ppdb_comparison.rds'))
gg_trichlorofon
```

@@

### Result: Single EC50 value for a specific test setting

@@

```{r fig.width=10, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_output.rds'))
gg_comparison
```

---
# Comparison: PPDB

```{r fig.width=10, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_ppdb_comparison.rds'))
gg_comparison
```

<img src="https://sitem.herts.ac.uk/aeru/ppdb/en/new_logo_small.jpg" width="250px" style="position:absolute; top:140px; right:50px;">

--
92% of Standartox values diverge by less than a factor of 10 from PPDB values

@@

<img src="http://3.bp.blogspot.com/-Wpp0vCJQDHo/U_ZMorXEynI/AAAAAAAAA7Y/Y-f-3brn99k/s1600/GBIF_logo_short_form.gif" width="120px" style="position:absolute; bottom:20px; left:70px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/worms.png" width="250px" style="position:absolute; bottom:30px; left:260px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/chebi.png" width="250px" style="position:absolute; bottom:140px; right:110px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/pubchem.png" width="250px" style="position:absolute; bottom:25px; right:90px;">
